Discovering governing reactions from concentration data

### 2018-08-27 docs/manuscript.tex
wip

    In our example proteins of type $\mathrm{A}$ regulate the $\mathrm{mRNA}_\mathrm{B}$ molecules, proteins of type $\mathrm{B}$ regulate the $\mathrm{mRNA}_\mathrm{A}$ molecules and proteins of type $\mathrm{C}$ regulate the $\mathrm{mRNA}_\mathrm{A}$ molecules. The network of all species and reactions is depicted in Figure \ref{fig:network}. This serves as reference model to generate the time series of concentrations.
    \begin{figure}
        \centering
        \includegraphics[width=.5\textwidth]{./figures_tex/scheme.pdf}
        \caption{The regulation network example described in Sec.~\ref{sec:generegulation}. \textbf{(a)}: Each circle depicts a species, each arrow corresponds to one reaction. Blue arrows denote transcription from DNA to mRNA, green arrows denote translation from mRNA to protein, and red arrows denote the regulatory network. \textbf{(b)}: Concentration timeseries generated from the reaction network shown in~(a). The initial condition prescribes positive concentration values only for B protein and $\mathrm{mRNA}_\mathrm{A}$ species. This initial condition is used in the subsequent sections for further analysis.}
        \label{fig:network}
    \end{figure}

@@

	First it is assumed that the concentration data can be obtained without noise and it is shown that while the minimization problem (\ref{method:minimizationproblem}) without regularization, i.e., $\alpha=0$, yields rates that fit well to the input data, the original rates cannot be recovered while adding $L_1$ regularization and a certain cutoff improves the situation and the original model can be recovered.

	In Section \ref{sec:case-2} the example data contains additive Gaussian noise. It is assumed that the initial state can be reproduced exactly and one has several measurements. It is shown that in the limit of small noise one can obtain a good fit and regularization helps in the reliability of the estimated reaction rates.

	The last example is described in Section \ref{sec:case-3} and can be seen as an extension of the situation in Section \ref{sec:case-3} to multiple initial conditions.

>>>>

    In our example proteins of type $\mathrm{A}$ regulate the $\mathrm{mRNA}_\mathrm{B}$ molecules, proteins of type $\mathrm{B}$ regulate the $\mathrm{mRNA}_\mathrm{A}$ molecules and proteins of type $\mathrm{C}$ regulate the $\mathrm{mRNA}_\mathrm{A}$ molecules. The network of all species and reactions is depicted in Figure \ref{fig:network}. This serves as reference model to generate the time series of concentrations.
    \begin{figure}
        \centering
        \includegraphics[width=.5\textwidth]{./figures_tex/scheme.pdf}
        \caption{The regulation network example described in Sec.~\ref{sec:generegulation}. \textbf{(a)}: Each circle depicts a species, each arrow corresponds to one reaction. Blue arrows denote transcription from DNA to $\mathrm{mRNA}$, green arrows denote translation from $\mathrm{mRNA}$ to protein, and red arrows denote the regulatory network. \textbf{(b)}: Concentration timeseries generated from the reaction network shown in~(a). The initial condition prescribes positive concentration values only for $\mathrm{B}$ protein and $\mathrm{mRNA}_\mathrm{A}$ species. This initial condition is used in the subsequent sections for further analysis.}
        \label{fig:network}
    \end{figure}

@@

	First it is assumed that the concentration data can be obtained without noise and it is shown that while the minimization problem (\ref{method:minimizationproblem}) without regularization, i.e., $\alpha=0$, yields rates that fit well to the input data, the original rates cannot be recovered while adding $L_1$ regularization and applying a cutoff recovers the underlying reaction network \textcolor{red}{(and rates?)}.

	In Section \ref{sec:case-2} the example data was generated using the Gillespie SSA \textbf{[cite]}. While the concentrations now contain stochastic noise, it is assumed that the initial state can be reproduced exactly and multiple measurements with that exact initial condition can be performed. It is shown that in the limit of many measurements a good fit can reliably be obtained.

	The last example is described in Section \ref{sec:case-3} and is an extension of the situation in Section \ref{sec:case-2} to multiple initial conditions. Due to more varied data and more statistics a good fit can be obtained with fewer measurements than in the case of just one initial condition.
